
\pagebreak
\phantomsection
\addcontentsline{toc}{section}{Trang thông tin luận văn tiếng Anh}
\section*{\centering \MakeUppercase{THESIS INFORMATION}}

Thesis title: OpenHuman: A conversational gesture synthesis system based on emotions and semantics \\
Speciality: Computer Science \\
Code: 8480104\\
Name of Master Student: Hoàng Minh Thanh \\
Academic year: 31\\
Supervisor: Associate Professor Ly Quoc Ngoc\\
At: VNUHCM - University of Science



\subsection*{1 SUMMARY}
In the context of the rapid development of big data and modern information systems, the use of Microsoft SQL Server (MSSQL) to manage online membership systems like ASP.NET Membership has begun to reveal significant limitations. ASP.NET Membership, originally designed to manage users and related information, has witnessed a considerable increase in the volume of data that needs to be processed, especially as the system continues to expand. However, when faced with large volumes of data and the demand for fast processing speeds, MSSQL often encounters performance issues, such as slow query speeds, inefficient resource management, and limited scalability.

These limitations not only degrade the user experience but also pose significant challenges for system administrators in maintaining and enhancing the performance of ASP.NET Membership. To address these issues, this thesis proposes and implements a solution to transition from MSSQL to the distributed database system Greenplum. This solution aims to significantly improve the performance and scalability of ASP.NET Membership, meeting the demands of big data processing and the increasingly high requirements of online membership management systems.

The experimental section of the thesis conducts rigorous tests to compare the performance of the system after transitioning to Greenplum with the original MSSQL system. The tests focus on critical tasks such as user search, registration, and login. Performance metrics such as query latency, processing speed, and scalability are carefully measured. The experimental results show that Greenplum offers significant improvements in processing speed and scalability, effectively meeting the stringent requirements of large data systems.

The thesis concludes that transitioning from MSSQL to Greenplum is an effective solution to enhance the performance and scalability of the ASP.NET Membership online management system. Additionally, the thesis opens up future research directions on integrating advanced data analytics tools and optimizing system architecture to meet the growing demands of modern web applications.


\subsection*{2 NOVELTY OF THESIS}
The thesis has achieved several significant results in the field of distributed database management, particularly in demonstrating the ability to improve performance and scalability when transitioning from MSSQL to Greenplum in the ASP.NET Membership system. Experimental results show that distributed databases, especially Greenplum, have significantly reduced query times and enhanced the processing performance of large data volumes. Additionally, the thesis proposes an effective process for transitioning from a centralized database system to a distributed system, covering everything from hardware preparation, software installation, to system configuration optimization.


\subsection*{3 APPLICATIONS/ APPLICABILITY/ PERSPECTIVE}

The thesis not only holds theoretical value but also opens up numerous practical applications in large data management, especially in high-performance and high-availability web systems. Businesses can apply this solution to enhance the performance of existing systems and meet future scalability demands. However, there remain several issues that require further research, such as optimizing fault tolerance and data security in larger distributed environments, as well as more deeply integrating data analytics and machine learning tools to fully exploit the potential of distributed database systems.

\begin{center}
    \begin{tabular}{c c}
        \textbf{SUPERVISOR} & \textbf{Master STUDENT} \\
        (Signature, full name) & (Signature, full name) \\
    \end{tabular}
    
    \vspace{6cm} % Điều chỉnh khoảng cách này nếu cần
    
    \textbf{CERTIFICATION} \\
    \textbf{CERTIFICATION UNIVERSITY OF SCIENCE} \\
    \textbf{PRESIDENT}
\end{center}

\pagebreak